Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
added to libpurple section
Stuff

\usepackage{url,xspace}
\newcommand\Motmot{\textsc{Motmot}\xspace}
\newcommand\libmotmot{\texttt{libmotmot}\xspace}
\newcommand\libpurple{\texttt{libpurple}\xspace}

@@

\begin{description}
  \item[Proposer election:]

@@

The bulk of the integration work was writing callbacks for the
\verb`motmot_init` function of \libmotmot.  Once these callbacks are written
correctly, \libmotmot handles most of the work of starting, sending, and
coordinating chats automatically.  These callbacks were, in almost all
instances, responsible for calling \libpurple functions, which handle the UI
aspect of the associated \libmotmot calls.  In order to pass relevant
information to our callbacks, we created a \verb`MotmotInfo` struct, a large
data struct that is used differently in different callbacks to get all the
necessary info to the \libpurple calls.

>>>>

\usepackage{enumitem,url,xspace}
\newcommand\Motmot{\textsc{Motmot}\xspace}
\newcommand\libmotmot{\texttt{libmotmot}\xspace}
\newcommand\libpurple{\texttt{libpurple}\xspace}

\setdescription{leftmargin=0pt}

@@

\begin{description}
  \item[Join, part, and election:]
    The original Paxos paper remarks on, but does not actually describe, a
    procedure for electing a Paxos system's designated proposer; nor does it
    describe mechanisms for adding and removing individuals from the system.
    These are all, however, necessary to the functionality of our consensus
    algorithm.  Election is necessary in order to ensure that the system makes
    progress past the prepare phase of Paxos, lest multiple participants
    attempt repeatedly to prepare over one another.  Join and part are required
    in order to support any usable notion of chat.

    In \libmotmot, we guarantee the consistency of joins, parts, and election
    results by baking them in to the standard commit protocol.

@@

The bulk of the integration work was writing callbacks for the
\verb`motmot_init` function of \libmotmot.  Once these callbacks are written
correctly, \libmotmot handles most of the work of starting, sending, and
coordinating chats automatically.  These callbacks were, in almost all
instances, responsible for calling \libpurple functions, which handle the UI
aspect of the associated \libmotmot calls.  In order to pass relevant
information to our callbacks, we created a \verb`MotmotInfo` struct, a large
data struct that is used differently in different callbacks to get all the
necessary info to the \libpurple calls. \verb`MotmotInfo` contained the info
necessary to mediate between \libpurple and \libmotmot. It contained both the
id of the chat which was necessary for \libpurple and the opaque data handle
necessary for \libmotmot.
